RadLib: a radiative heat transfer model library for CFD

### 2020-12-21 manuscript/manuscript.tex
more...

The RCSLW model uses the notion of \emph{rank correlation} to compute this variation in $C_j$ and $\tilde{C}_j$. Solovjov et~al.~\cite{Solovjov_2017} define two spectra at thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wavenumber sets $H_1(\BS{\phi}_1)$ and $H_2(\BS{\phi}_2)$ are equal, where 
%
\begin{linenomath}
\begin{align}
    H_1(\BS{\phi}_1)&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}, \\
    H_2(\BS{\phi}_2)&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}. 
\end{align}
\end{linenomath}
%

Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and denote $C_\eta(\hat{\eta},\BS{\phi}_1)$ as $C_1$, and similarly for $C_2$; then we have
%
\begin{linenomath}
    \begin{align} \label{e:albdf2}
        F(C_1,\BS{\phi}_1,T) &= \frac{1}{\sigma T^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
        F(C_2,\BS{\phi}_2,T) &= \frac{1}{\sigma T^4}\int_{H_2}E_b(\eta,T_r)d\eta.
    \end{align}
\end{linenomath}
%

>>>>

The RCSLW model uses the notion of \emph{rank correlation} to compute this variation in $C_j$ and $\tilde{C}_j$. Solovjov et~al.~\cite{Solovjov_2017} define two spectra at states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wavenumber sets $H_1(\BS{\phi}_1)$ and $H_2(\BS{\phi}_2)$ are equal, where 
%
\begin{linenomath}
\begin{align}
    H_1(\BS{\phi}_1)&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}, \\
    H_2(\BS{\phi}_2)&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}. 
\end{align}
\end{linenomath}
%

Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$, and similarly for $\hat{C}_2$; then we have
%
\begin{linenomath}
    \begin{align} \label{e:albdf2}
        F(\hat{C}_1,\BS{\phi}_1,T) &= \frac{1}{\sigma T^4}\int_{H_1(\BS{\phi_1})}E_b(\eta,T_r)d\eta, \\
        F(\hat{C}_2,\BS{\phi}_2,T) &= \frac{1}{\sigma T^4}\int_{H_2(\BS{\phi_1})}E_b(\eta,T_r)d\eta.
    \end{align}
\end{linenomath}
%
